Analysis after review

### 2020-06-01 reports/DRM_exp/analysis_DRM_after_review.Rmd
code cleanup

```{r}
prot_dir <- "data/exp_DRM1/protocols/"
fs <- list.files(prot_dir, full.names = T, pattern = "*.csv") %>% str_subset("P000", negate = T)

@@

@@

df_dist_target_images %>% 
ggplot(aes(x = as.character(correct), y = dist_to_target_image)) + stat_summary(fun.data = "mean_cl_boot")

p <- df_dist_target_images %>% 
  ggplot(aes(x = dist_to_target_image, y = correct)) + stat_summary(fun.data = "mean_cl_boot") + 
  theme(aspect.ratio = 1) + 
  xlab("Interval between presentations") + 
  ylab("Accuracy")
p
ggsave(file.path(plots_dir, "Figure6xx_target_distance.svg"), p, width = 6, height = 6)
df_dist_target_images %>% 
  filter(dist_to_target_image > 5) %>% 
ggplot(aes(x = dist_to_target_image, y = correct)) + stat_summary(fun.data = "mean_cl_boot")

df_dist_target_images %>% filter(dist_to_target_image > 5) %>% cor.test(~correct+dist_to_target_image,.)
```

## Average accuracy per image

```{r}
p <- df %>% group_by(type,img_name) %>% 
  summarize(correct = mean(correct, na.rm = T), dist_to_proto = mean(dist_to_proto)) %>% 
  ggplot(aes(x = dist_to_proto, y = correct, col = type)) + 
  geom_point(alpha = 0.2) + stat_smooth(method = "lm") +
  theme(aspect.ratio = 1) + 
  xlab("Distance to visual prototype") + 
  ylab("Accuracy")
p
ggsave(file.path(plots_dir, "FXXScatter.svg"), p, width = 6, height = 6)

@@

## Correlation of distance from prototype with accuracy

As we have for each test scene ditance to prototype and accuracy, we can compute correlation between those variables. I am not sure, whether we can aggregate somehow to get averaged accuracies?

Neverethless, we computed correlations for all scenes, followed by correlation for each type separately. We also show one figure with correlations for each layer.

```{r Correlation of distance from prototype with accuracy }
f <- function(dfx) {
  dfx %>% group_by(img_name) %>% summarize(correct = mean(correct), dist_to_proto = mean(dist_to_proto),dist_to_proto_conv3 = mean(dist_to_proto_conv3),
                                           dist_to_proto_conv5 = mean(dist_to_proto_conv5))  
}
f2 <- function(dfx) {
  dfx %>% group_by(type,img_name) %>% summarize(correct = mean(correct), dist_to_proto = mean(dist_to_proto),dist_to_proto_conv3 = mean(dist_to_proto_conv3),
                                           dist_to_proto_conv5 = mean(dist_to_proto_conv5))  
}

rbind( 
cor.test(~dist_to_proto+correct, df %>% f()) %>% broom::tidy() %>% mutate(layer="fc7", type = "all"),
cor.test(~dist_to_proto+correct, df %>% filter(type == "far distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="fc7", type = "far distractor"),
cor.test(~dist_to_proto+correct, df %>% filter(type == "close distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="fc7", type = "close distractor"),
cor.test(~dist_to_proto+correct, df %>% filter(type == "target") %>% f()) %>% broom::tidy() %>% mutate(layer="fc7", type = "all", type = "target"),
cor.test(~dist_to_proto_conv5+correct, df %>% f()) %>% broom::tidy() %>% mutate(layer="conv5", type = "all"),
cor.test(~dist_to_proto_conv5+correct, df %>% filter(type == "far distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="conv5", type = "far distractor"),
cor.test(~dist_to_proto_conv5+correct, df %>% filter(type == "close distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="conv5", type = "close distractor"),
cor.test(~dist_to_proto_conv5+correct, df %>% filter(type == "target") %>% f()) %>% broom::tidy() %>% mutate(layer="conv5", type = "all", type = "target"),
cor.test(~dist_to_proto_conv3+correct, df %>% f()) %>% broom::tidy() %>% mutate(layer="conv3", type = "all"),
cor.test(~dist_to_proto_conv3+correct, df %>% filter(type == "far distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="conv3", type = "far distractor"),
cor.test(~dist_to_proto_conv3+correct, df %>% filter(type == "close distractor") %>% f()) %>% broom::tidy() %>% mutate(layer="conv3", type = "close distractor"),
cor.test(~dist_to_proto_conv3+correct, df %>% filter(type == "target") %>% f()) %>% broom::tidy() %>% mutate(layer="conv3", type = "all", type = "target")) %>% 
  select(layer, type, estimate, conf.low, conf.high, p.value) %>% 
  knitr::kable(digits = 3, caption ="correlation between accuracy and distance to prototype")

df1 <- df %>% f2() %>% pivot_longer(cols = starts_with("dist_to_proto"),names_to = "layer", values_to = "distance_to_proto")

df1_gr <- df1 %>% 
  group_by(layer, type) %>% 
  do(cor.test(.$distance_to_proto, .$correct) %>% broom::tidy()) %>% 
  ungroup() %>% 
  mutate(layer = recode(layer, dist_to_proto = "fc7", dist_to_proto_conv3 = "conv3", dist_to_proto_conv5 = "conv5")) %>% 
  mutate(layer = factor(layer, levels = c("conv3", "conv5", "fc7"))) 
df1_all <- df1 %>% 
  group_by(layer) %>% 
  do(cor.test(.$distance_to_proto, .$correct) %>% broom::tidy()) %>% 
  ungroup() %>% 
  mutate(layer = recode(layer, dist_to_proto = "fc7", dist_to_proto_conv3 = "conv3", dist_to_proto_conv5 = "conv5")) %>% 
  mutate(layer = factor(layer, levels = c("conv3", "conv5", "fc7"))) %>% 
  mutate(type = "all")
pd <- position_dodge(0.1, seed = 123)
p <- df1_gr %>% 
  arrange(type,layer) %>% 
  ggplot(aes(x = layer, y = estimate, col = type, group = type)) + 
  geom_point(position =  pd)+#position =  position_jitter(width = 0.1, seed = 123)) + 
  geom_line(position =  pd)+#position = position_jitter(width = 0.1, seed = 123)) + 
  geom_linerange(aes(ymin = conf.low, ymax = conf.high),position =  pd)+
  ylab("correlation") +
  ggtitle("Correlation between accuracy and distance to prototype")+
  geom_point(data = df1_all %>% arrange(type,layer), aes(x = layer, y = estimate, group = 1), col = "black") + 
  geom_line(data = df1_all %>% arrange(type,layer), aes(x = layer, y = estimate, group = 1), col = "black") + 
  geom_linerange(data = df1_all %>% arrange(type,layer), aes(ymin = conf.low, ymax = conf.high), col = "black") +
  theme(aspect.ratio = 1)
ggsave(file.path(plots_dir, "FigureXX_layers_correlation.svg"), p, width = 6, height = 6)
```

Figure shows, that correlation is about the same for different layers with exception of far distracators, which decreases with higher layers. Black is for all data

### Distances from tgt images - fc7

## Average distance to target

We can compute distance to targets for each test scene. From these values, we can compute average. Because each layer has different ranges, we normalize the distances by dividint them by distance to the target. Lower values than 1 means, that given scene type is closer to targets than targets themselves (e.g. their are more in center).

```{r}
gt0 <- function(x) {x >0}

df2_tgt <- df2 %>% 
  rowwise() %>% 
  mutate(mean_tgt_dist = unlist(distance_to_targets) %>% mean(),
         min_tgt_dist = unlist(distance_to_targets) %>% min(),
         min_tgt_dist_no0 = unlist(distance_to_targets) %>% Filter(gt0,.) %>% min())

df2_tgt_agg1 <- df2_tgt %>% 
    mutate(layer = recode(layer, dist_to_tgts = "fc7", dist_to_tgts_conv3 = "conv3", dist_to_tgts_conv5 = "conv5")) %>% 
    mutate(layer = factor(layer, levels = c("conv3", "conv5", "fc7")))

df2_tgt_agg1 %>% 
  ungroup() %>% 
  filter(layer == "fc7") %>% 
  group_by(img_name,type) %>% 
  summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0)) %>% 
  ggplot(aes(x = min_tgt_dist_no0, y = correct, col = type)) +
  geom_point(alpha = 0.2) + stat_smooth(method = "lm") +
  theme(aspect.ratio = 1) + 
  xlab("Minimum distance to target (0 exlucded)") + 
  ylab("Accuracy")

df2_tgt_agg1 %>% 
  ungroup() %>% 
  filter(layer == "conv5") %>% 
  group_by(img_name,type) %>% 
  summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0), dist_to_proto = mean(dist_to_proto)) %>% 
  ggplot(aes(x = min_tgt_dist_no0, y = correct, col = type)) +
  geom_point(alpha = 0.2) + stat_smooth(method = "lm") +
  theme(aspect.ratio = 1) + 
  xlab("Minimum distance to target (0 exlucded)") + 
  ylab("Accuracy")

df2_tgt_agg1 %>% 
  ungroup() %>% 
  filter(layer == "fc7") %>% 
  group_by(img_name) %>% 
  summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0), dist_to_proto = mean(dist_to_proto)) %>% 
  cor.test(~min_tgt_dist_no0+dist_to_proto,.)

df2_tgt_agg1 %>% 
  ungroup() %>% 
  filter(layer == "fc7") %>% 
  group_by(img_name) %>% 
  summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0), dist_to_proto = mean(dist_to_proto)) %>% 
  cor.test(~correct+dist_to_proto,.)
df2_tgt_agg1 %>% 
  ungroup() %>% 
  filter(layer == "fc7") %>% 
  group_by(img_name,type) %>% 
  summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0), dist_to_proto = mean(dist_to_proto)) %>% 
  group_by(type) %>% 
  do(cor.test(~correct+dist_to_proto,.) %>% broom::tidy())

p <- df2_tgt_agg1 %>% 
    ungroup() %>% 
    filter(layer == "fc7") %>% 
    group_by(img_name,type) %>% 
    summarize(correct = mean(correct),  min_tgt_dist_no0 = mean(min_tgt_dist_no0), dist_to_proto = mean(dist_to_proto)) %>%
  ggplot(aes(x = dist_to_proto, y = min_tgt_dist_no0, col = type)) + 
  geom_point() + 
  theme(aspect.ratio = 1) +
  xlab("Distance to visual prototype") + 
  ylab("Minimum distance to target (0 exlucded)")
p
ggsave(file.path(plots_dir, "FigureXXDistances_right.svg"), p, width = 6, height = 6)

## Minimum distance to target

Alternativelly, we can compute minimum distance of presented scene to one of the targets. We are removing zero distances, as in case of target queries, this minimum would be 0.

```{r Min distance to target}
df2_tgt_agg2_ci <- df2_tgt_agg1 %>% 
  group_by(layer,type) %>% 
  summarize(m=Hmisc::smean.cl.boot(min_tgt_dist_no0)[1],lower =Hmisc::smean.cl.boot(min_tgt_dist_no0)[2], upper = Hmisc::smean.cl.boot(min_tgt_dist_no0)[3])

df2_tgt_agg2_ci %>% 
  group_by(layer) %>% 
  mutate(m = m/m[type=="target"]) %>% 
  ggplot(aes(x=layer, y=m,col = type, group = type)) + 
  geom_point()+geom_line() +
  ggtitle("Minimum distance to targets (identities excluded)")

Figure shows that types of images get closer to each other in lower layers.

```{r select examples}

set.seed(19763) 
df_names <- df %>% filter(subject_id == 1, grp_order == 3) %>% group_by(type) %>% sample_n(5)

df %>% filter(img_name %in% df_names$img_name) %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))
```

## Compare to category center

```{r Compare to category center}
cr <- df %>% rename(dist_to_proto_fc7 = dist_to_proto) %>% select(starts_with("dist_to_proto"),starts_with("dist_to_cat_center"), correct, img_name) %>% 
  group_by(img_name) %>% 
  summarize_each(mean) %>% 
  ungroup() %>% 
  select(-img_name) %>% 
  as.matrix() %>% 
  Hmisc::rcorr()

cr$r

cr_close <- df %>% rename(dist_to_proto_fc7 = dist_to_proto) %>% 
  filter(type == "close distractor") %>% 
  select(starts_with("dist_to_proto"),starts_with("dist_to_cat_center"), correct, img_name) %>% 
  group_by(img_name) %>% 
  summarize_each(mean) %>% 
  ungroup() %>% 
  select(-img_name) %>% 
  as.matrix() %>% 
  Hmisc::rcorr()

cr_close$r %>% knitr::kable(digits = 2)

cr_targets <- df %>% rename(dist_to_proto_fc7 = dist_to_proto) %>% 
  filter(type == "target") %>% 
  select(starts_with("dist_to_proto"),starts_with("dist_to_cat_center"), correct, img_name) %>% 
  group_by(img_name) %>% 
  summarize_each(mean) %>% 
  ungroup() %>% 
  select(-img_name) %>% 
  as.matrix() %>% 
  Hmisc::rcorr()

cr_targets$r %>% knitr::kable(digits = 2)

p <- df %>% group_by(type,img_name) %>% 
  summarize(correct = mean(correct, na.rm = T), dist_to_cat_center_fc7 = mean(dist_to_cat_center_fc7)) %>% 
  ggplot(aes(x = dist_to_cat_center_fc7, y = correct, col = type)) + 
  geom_point(alpha = 0.2) + stat_smooth(method = "lm") +
  theme(aspect.ratio = 1) + 
  xlab("Distance to visual prototype") + 
  ylab("Accuracy")
p
```

## Model Distance to targets

```{r}
df$dist_to_tgts <- purrr::map2(df$dist_to_tgts, df$avg_dist_between_tgts, ~.x/.y) # normalize distances

dist_vals_targets <- df %>% 
  filter(type == "target") %>% 
  pull(dist_to_tgts) %>% 
  unlist()

dist_vals_close_dist <- df %>% 
  filter(type == "close distractor") %>% 
  pull(dist_to_tgts) %>% 
  unlist()

dist_vals_far_dist <- df %>% 
  filter(type == "far distractor") %>% 
  pull(dist_to_tgts) %>% 
  unlist()

df_dist_vals <- tibble(type = c(rep("target", length(dist_vals_targets)),
                                rep("close distractor", length(dist_vals_close_dist)),
                                rep("far distractor", length(dist_vals_far_dist))),
                       value = c(dist_vals_targets, dist_vals_close_dist, dist_vals_far_dist)) %>% 
  filter(value > 0)

df_dist_vals %>% 
  ggplot(aes(x = value, col = type)) + geom_freqpoly()

df$model_dist_tgt_02 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.2)) # normalize distances
df$model_dist_tgt_03 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.3)) # normalize distances
df$model_dist_tgt_04 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.4)) # normalize distances
df$model_dist_tgt_05 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.5)) # normalize distances
df$model_dist_tgt_06 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.6)) # normalize distances
df$model_dist_tgt_07 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.7)) # normalize distances
df$model_dist_tgt_08 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.8)) # normalize distances
df$model_dist_tgt_09 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<0.9)) # normalize distances
df$model_dist_tgt_1 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<1)) # normalize distances
df$model_dist_tgt_12 <- purrr::map_dbl(df$dist_to_tgts, ~any(.x<1.2)) # normalize distances

dfx <- df %>% 
  pivot_longer(cols = starts_with("model_dist_tgt"), names_to = "model", values_to = "accuracy") %>% 
  mutate(accuracy = if_else(type == "target",accuracy, 1-accuracy))

dfx %>% 
  ggplot(aes(x = type, y = accuracy, col = model, group = model)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")

dfx %>% 
  group_by(img_name, model, type) %>% 
  summarize(correct = mean(correct), accuracy = mean(accuracy)) %>% 
  mutate(accuracy = jitter(accuracy)) %>% 
  group_by(model, type) %>% 
  do(cor.test(~accuracy+correct,.) %>% broom::tidy()) %>% 
  filter(type == "close distractor")

## Divide distractors by distance to targets - min no0

```{r}
divide_into_groups_tgt_dist <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$min_tgt_dist)

  dfxx_notgt$model_type[rnk <= 5] <- "close_tgt"
  dfxx_notgt$model_type[rnk > 5]  <- "far_tgt"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_tgt <- df2_tgt %>% ungroup() %>% distinct()
df2_tgt_modeldist <- df2_tgt %>% 
  filter(layer == "dist_to_tgts") %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_tgt_dist(.))

df2_tgt_modeldist %>% xtabs(~type+model_type,.) %>% prop.table(1)
df2_tgt_modeldist %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()
df2_tgt_modeldist %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

df2_tgt_modeldist %>% filter(type != "target") %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))

## Divide distractors by distance to targets - mean

```{r}
divide_into_groups_tgt_dist_mean <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$mean_tgt_dist)

  dfxx_notgt$model_type[rnk <= 5] <- "close_tgt"
  dfxx_notgt$model_type[rnk > 5]  <- "far_tgt"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_tgt <- df2_tgt %>% ungroup() %>% distinct()
df2_tgt_modeldist_mean <- df2_tgt %>% 
  filter(layer == "dist_to_tgts") %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_tgt_dist_mean(.))

df2_tgt_modeldist_mean %>% xtabs(~type+model_type,.) %>% prop.table(1)
df2_tgt_modeldist_mean %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()
df2_tgt_modeldist_mean %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

df2_tgt_modeldist_mean %>% filter(type != "target") %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))

## Divide distractors by memorability

```{r}
df_perimage <- df %>% group_by(img_name,type) %>% summarize(m = mean(correct), sd = sd(correct)) %>% arrange(-m)
mem_imgnames <- read_csv(here("data/exp_DRM1/memorability/memorability_imgnames.txt"), col_names = F)
mem_values <- read_csv(here("data/exp_DRM1/memorability/memorability_all.txt"), col_names = F)

@@

divide_into_groups_memorability <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$mem_score)

  dfxx_notgt$model_type[rnk <= 5] <- "low memorability"
  dfxx_notgt$model_type[rnk > 5]  <- "high memorability"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_modelmem <- dfm %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_memorability(.))

df2_modelmem %>% xtabs(~type+model_type,.) %>% prop.table()
df2_modelmem %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()

df2_modelmem %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

## Divide distractors by fc7

divide_into_groups_dist_to_proto <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$dist_to_proto)

  dfxx_notgt$model_type[rnk <= 5] <- "close_to_prototype"
  dfxx_notgt$model_type[rnk > 5]  <- "far_to_prototype"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_modeldisttoproto <- df %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_dist_to_proto(.))

df2_modeldisttoproto %>% xtabs(~type+model_type,.)
df2_modeldisttoproto %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()

df2_modeldisttoproto %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

## Divide distractors by conv3

divide_into_groups_dist_to_proto_conv3 <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$dist_to_proto_conv3)

  dfxx_notgt$model_type[rnk <= 5] <- "close_tgt"
  dfxx_notgt$model_type[rnk > 5]  <- "far_tgt"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_modeldisttoproto3 <- df %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_dist_to_proto_conv3(.))

df2_modeldisttoproto3 %>% xtabs(~type+model_type,.)
df2_modeldisttoproto3 %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()

df2_modeldisttoproto3 %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

df2_tgt_modeldist %>% filter(type != "target") %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))

## Divide distractors by conv5

divide_into_groups_dist_to_proto_conv5 <- function(dfxx) {

  dfxx_notgt <- dfxx %>% filter(type != "target") %>% mutate(model_type = NA)

  rnk <- rank(dfxx_notgt$dist_to_proto_conv5)

  dfxx_notgt$model_type[rnk <= 5] <- "close_tgt"
  dfxx_notgt$model_type[rnk > 5]  <- "far_tgt"

  dfxx %>% 
    left_join(dfxx_notgt %>% select(img_name,model_type), by="img_name") %>% 
    mutate(model_type = if_else(type == "target","target",model_type))
}

df2_modeldisttoproto5 <- df %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_dist_to_proto_conv5(.))

df2_modeldisttoproto5 %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% prop.table(1)
df2_modeldisttoproto5 %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()

df2_modeldisttoproto5 %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

df2_tgt_modeldist %>% filter(type != "target") %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))

@@

cor.test(~ dist_to_cat_center_fc7+ dist_to_cat_center_conv5, df)
cor.test(~ dist_to_cat_center_fc7+ dist_to_cat_center_conv3, df)

cor.test(~ dist_to_cat_center_fc7+ dist_to_proto, df)
cor.test(~ dist_to_cat_center_conv5+ dist_to_proto_conv5, df)
cor.test(~ dist_to_cat_center_conv3+ dist_to_proto_conv3, df)
```

### Compare models

```{r}
df2_modelmem1 <- 
  df2_modelmem %>% 
    ungroup() %>% 
    select(subject_id, trial_id, category_centroid_type = type, memorability_model =model_type, correct, category)

df2_modeldisttoproto31 <- 
  df2_modeldisttoproto3  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto3 =model_type, correct, category)

df2_modeldisttoproto51 <- 
  df2_modeldisttoproto5  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto5 =model_type, correct, category)

df2_tgt_modeldist1 <- 
  df2_tgt_modeldist  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, min_dist_to_tgt =model_type, correct, category) 
df_models_res <- df2_modelmem1 %>% 
  left_join(df2_modeldisttoproto31, by = c("subject_id", "trial_id", "correct","category")) %>% 
  left_join(df2_modeldisttoproto51, by = c("subject_id", "trial_id", "correct","category")) %>% 
  left_join(df2_tgt_modeldist1, by = c("subject_id", "trial_id", "correct","category")) %>% 
  filter(category_centroid_type != "target")

df_models_res_longer <- df_models_res %>% 
  pivot_longer(cols = c(category_centroid_type, min_dist_to_tgt, dist_to_proto5, dist_to_proto3, memorability_model))

XXtab <- df_models_res_longer %>% 
  group_by(name,value) %>% 
  summarize(FA = sprintf("%.2f", mean(1-correct)))

XXtab

glmm_null_model <- df_models_res %>% glmer(correct~1+(1|subject_id) + (1|category), ., family = binomial())

glmm_orig_model <- df_models_res %>% glmer(correct~category_centroid_type+(1+category_centroid_type|subject_id) + (1|category), ., family = binomial())
glmm_dist_to_tgt <- df_models_res %>% glmer(correct~min_dist_to_tgt + (1+min_dist_to_tgt|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv5 <- df_models_res %>% glmer(correct~dist_to_proto5 + (1+dist_to_proto5|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv3 <- df_models_res %>% glmer(correct~dist_to_proto3 + (1+dist_to_proto3|subject_id) + (1|category),., family = binomial())
glmm_memorability <- df_models_res %>% glmer(correct~memorability_model + (1+memorability_model|subject_id) + (1|category),., family = binomial())
models_list <- list(glmm_null_model,glmm_orig_model,glmm_dist_to_tgt,glmm_dist_to_proto_conv5,glmm_dist_to_proto_conv3,glmm_memorability)
models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_conditional") %>% 
  round(2)

models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_marginal") %>% 
  round(2)

models_list %>% 
  map_dbl(AIC)
```

## Context entropy

```{r}
cont_entropy <- read_csv(here("data/exp_DRM1/cats_entrophy.csv"), col_names = F) %>% rename(category = X1, cont_entropy = X2) %>% mutate(category = str_replace(category, "_", " "))
df_cont_entropy <- df %>% left_join(cont_entropy, by = "category") 
df_cont_entropy %>% 
  ggplot(aes(x = category, y = correct, col = type, group = type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")

df_cont_entropy %>% 
  filter(type != "target") %>% 
  group_by(category,type) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  group_by(category) %>% 
  summarize(diff_FA = FA[type == "close distractor"]-FA[type == "far distractor"],
            cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = diff_FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()

>>>>

```{r}
prot_dir <- here("data/exp_DRM1/protocols/")
fs <- list.files(prot_dir, full.names = T, pattern = "*.csv") %>% str_subset("P000", negate = T)

@@

df2_tgt <- df2 %>% 
  rowwise() %>% 
  mutate(mean_tgt_dist = unlist(distance_to_targets) %>% mean(),
         min_tgt_dist = unlist(distance_to_targets) %>% min(),
         min_tgt_dist_no0 = unlist(distance_to_targets) %>% Filter(gt0,.) %>% min()) %>% 
  distinct()

@@

p <- df_dist_target_images %>% 
  ggplot(aes(x = dist_to_target_image, y = correct)) + stat_summary(fun.data = "mean_cl_boot") + 
  theme(aspect.ratio = 1) + 
  xlab("Interval between presentations") + 
  ylab("Accuracy")
p

@@

# Alternative models

## Distance to proto - conv3

df2_modeldisttoproto3 <- df %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups(.,"dist_to_proto_conv3","close_tgt","far_tgt"))
```

## Distance to proto - conv5

df2_modeldisttoproto5 <- df %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups(.,"dist_to_proto_conv5","close_tgt","far_tgt"))
```

## Distance to targets - fc7

df2_tgt_modeldist <- df2_tgt %>% 
  filter(layer == "dist_to_tgts") %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups(., "min_tgt_dist", "close_tgt", "far_tgt"))
```

## Memorability model

df_perimage <- df %>% group_by(img_name,type) %>% summarize(m = mean(correct), sd = sd(correct)) %>% arrange(-m)
mem_imgnames <- read_csv(here("data/exp_DRM1/memorability/memorability_imgnames.txt"), col_names = F)
mem_values <- read_csv(here("data/exp_DRM1/memorability/memorability_all.txt"), col_names = F)

@@

df2_modelmem <- dfm %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups(.,"mem_score", "low_memorable","high_memorable"))

@@

c_cat_center_conv5 <- cor.test(~dist_to_cat_center_fc7+dist_to_cat_center_conv5, df, method = "sp")
c_cat_center_conv3 <- cor.test(~dist_to_cat_center_fc7+dist_to_cat_center_conv3, df, method = "sp")

c_fc7 <- cor.test(~ dist_to_cat_center_fc7+ dist_to_proto, df, method = "sp")
c_conv5 <- cor.test(~ dist_to_cat_center_conv5+ dist_to_proto_conv5, df, method = "sp")
c_conv3 <- cor.test(~ dist_to_cat_center_conv3+ dist_to_proto_conv3, df, method = "sp")

conv3_changed <- df2_modeldisttoproto3 %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% prop.table(1)
conv5_changed <- df2_modeldisttoproto5 %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% prop.table(1)

tgt_changes <- df2_tgt_modeldist %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% prop.table(1)
mem_changed <- df2_modelmem  %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% prop.table(1)
```

The first two models aimed to explore whether the high false alarm rate was driven by high level features (original fc7 model) or by low level features. We evaluated each image in convolutional layers conv3 and conv5, which represent the scenes’ lower visual features relative to their more semantic features in fc7 (models conv3 and conv5). Consequently, the proximity in higher levels does not need to be reflected in lower levels or vice versa. For example, the distances between scenes and their corresponding category centroids differ from fc7 (conv5: Spearman $\rho$ = `r c_cat_center_conv5$estimate %>% round(2)`; conv5: Spearman $\rho$ = `r c_cat_center_conv3$estimate %>% round(2)`). However, due to the selection of experimental stimuli (choosing targets closer to category centroids), the distances between visual prototype (the center of 15 targets) and category centroids are highly correlated. This correlation is preserved in lower layers (fc7: Spearman’s $\rho$ = `r c_fc7$estimate %>% round(2)`, conv5: Spearman’s $\rho$ = `r c_conv5$estimate %>% round(2)`, conv3: Spearman’s $\rho$ = `r c_conv3$estimate %>% round(2)`). When we again divided the distractors into close and far categories, the classification of distractors changed only in `r (100*conv5_changed[1,2]) %>% round(0)`% of cases for conv5 and `r (100*conv3_changed[1,2]) %>% round(0)`% of cases for conv3.

An alternative participant strategy for responding in the test phase would be to compare each presented scene with one of the targets. In such a case, the false alarm rate should be higher for scenes closer to one of the targets. Therefore, for each distractor, we computed the minimum distance to one of the targets (distance-to-targets model). However, as the targets were selected based on their proximity to the category centroid, this approach yielded a similar division of distractors into close and far (only `r (100*tgt_changes[1,2]) %>% round(0)`% of distractors were classified into the opposite category).

The final alternative model relies on estimated memorability (memorability model; Isola, Xiao, Torralba, & Oliva, 2011). We divided the scenes into lower and higher memorable scenes. Memorability is good candidate for predicting the task, because it has been demonstrated that memorable images show good perceptual organization (Goetschalckx, Moors, Vanmarcke, & Wagemans, 2018) and are quickly categorizable (Broers, Potter, & Nieuwenstein, 2018). Therefore, we evaluated the photographs using trained CNN MemNet, which can predict memorability resembling human performance (Khosla et al., 2015) . Although FIGRIM dataset contained ground-truth memorability scores for the subset of images, we decided to use estimated scores instead from MemNet instead as we needed memorability score for all images. Dividing scenes into groups with higher/lower memorability classified `r (100*mem_changed[1,1]) %>% round(0)`% close distractors as highly memorable, while for far distractors, it classified `r (100*mem_changed[2,1]) %>% round(0)`% of scenes as high memorable.

Evaluation of all the models showed similar results with weak explanatory power. For computation of the determination coefficient, we used formulas suggested by Nakagawa, Johnson, and Schielzeth (2017). This approach computed two versions of R2: conditional (model including both fixed and random effects) and marginal (including fixed effect only). Additionally, we also included a null model which has random factors only. As visualized in Table 1, the model distance to target showed the same results as the original model. Meanwhile, models relying on lower features conv5 and conv3 showed a decreasing FA rate with increasing depth. The memorability model showed the lowest fit.

```{r Table 1: False alarms for each of the alternative models }
print_table1()
```
